---
title: "Learning networks"
output: 
  html_document: 
    number_sections: yes
    theme: journal
---

```{r message=FALSE}
library(igraph)
```

# Basics
## Notation
Network g comprised of vertices V and edges E

## Creating graphs

### Literal definition

```{r}
g <- graph_from_literal(A:B-+C-+D-+E, F++G)
plot(g+graph_from_literal(E-+F,G-+A))
```

### Adjacency matrix
TODO: Generate adjacency matrices by taking into account that edges can be weighted or unweighted and directed or undirected

Adjacency matrix A
```{r}
set.seed(6)
adjm <- matrix(sample(0:1, 9, replace=TRUE, prob=c(0.9,1)), ncol=3)
adjm
plot(graph.adjacency(adjm))
```

## Complexity
Generally there are n(n-1)/2 (n choose 2) possible links, and 2^(n(n-1)/2) possible networks on n nodes

TODO: Simulate number of possible networks
```{r}
n <- 4
n*(n-1)/2
choose(n, 2)

```

# Centrality

## Degree: Connectedness
How "connected" is a node?

To normalize divide by n-1

```{r}

```

## Closeness
Relative distances to other nodes

(n‐1)/∑jl(i,j)
