---
title: "Problem Set 1"
output: 
  html_document: 
    theme: united
---

```{r message=FALSE}
library(igraph)
```
# Q1
Given a network (N,g), define its complement to be the network (N,g′), such that (ij∈g′) if and only if (ij∉g). 

Which statement is correct of networks with at least four nodes?

a) A network that is connected has an empty complement.

b) If a network is connected, then its complement is also connected.

c) There is a network such that both itself and its complement are connected.

TODO: Draw matrix and its complement

# Q2 - Q6
If g2 is the matrix on right, which of the following network could be represented by g?

```{r}

```

# Q7
What is the "Average degree"?

```{r}
v <- read.table('data/soceconetsps1', skip=1, nrows=135)
e <- read.table('data/soceconetsps1', skip=137, col.names=c('src','dest','smth'))
head(e)

g <- graph.empty(n=nrow(v), directed=FALSE)
for (idx in 1:nrow(e)) {
  g <- g + edge(e[idx,1], e[idx,2])  
}
plot(g)

mean(degree(g))
```

# Q8
What is the "Diameter"?

```{r}
diameter(g)
```

# Q9
What is the "Maximum Clustering"?

```{r}
lt <- transitivity(g, type="local")

max(lt, na.rm=TRUE)
```

# Q10
What is the "Minimum Clustering"? [Note: Please report the minimal non-zero clustering.]

```{r}
min(lt[lt > 0], na.rm=TRUE)
```
