---
title: "Problem Set 2"
output: 
  html_document: 
    theme: united
---

```{r message=FALSE}
library(igraph)
```
# Questions 1-3
Answer questions 1 to 3 based on the following network, which is a Erdos-Renyi random network with 7 nodes and average degree equal to 2  

```{r}
set.seed(6)
g <- graph_from_literal(1-4, 1-7, 2-4, 2-5, 3-5, 4-7, 6-7)
n <- length(V(g))
plot(g)
```

Which of the node(s) have the largest Degree centrality?
```{r}
degree(g)
```

What is the Closeness centrality for Node 2? 
```{r}
# manually
sumlij <- 2*1 + 3*2 + 1*3
(n-1)/sumlij
# igraph
closeness(g, "2", normalized=T)
```

Which of the node(s) have largest Betweenness centrality?
```{r}
betweenness(g)
```

# Q5

# Questions 6-8

```{r}
v <- read.table('data/soceconetsps2', skip=1, nrows=80, col.names=c('name','label','V1','V2','V3'))
e <- read.table('data/soceconetsps2', skip=82, col.names=c('from','to','V1'))
head(e)

g <- graph.data.frame(e[ ,1:2], directed=TRUE, vertices=v[ ,1:2])
plot(g)
```

Which of the following country has the maximum closeness centrality?

[Treat the graph as directed. Calculate centralities in the whole network, instead of the sub-network consisting of the five countries listed in the options.]

```{r}
ccl <- sapply(c('Germany','Italy','Japan','United States','China'), function(x) closeness(g, vids=V(g)$label==x))
ccl
max(ccl)
```

Which of the following country has the maximum "Betweenness centrality"?

```{r}
bcl <- sapply(c('Germany','Brazil','Argentina','United States','China'), function(x) betweenness(g, v=V(g)$label==x))
max(bcl)
```

# Q8
For this question you will need to generate some Poisson (Erdos-Renyi G(n,p)) random networks. 

You should generate several (undirected) Poisson random networks with 400 nodes, and with different average degrees.

Please indicate with which of the following average degrees the networks you generated turned out to be connected:

* 400 nodes and average degree = 1;
* 400 nodes and average degree = 5;
* 400 nodes and average degree = 10;
* 400 nodes and average degree = 20;

(This problem contains randomness, and so you may want to generate some number of networks for each case, just to be sure:). If you generate at least ten networks in each case, your probability of accidentally getting the wrong answer will be negligible.)

In answering this question, you should be able to easily relate your results to "A Threshold Theorem" mentioned in our lecture.

[Since Gephi does not have an option for ``average degree'', you need to choose "wiring probability" p instead of "average degree". Please notice that avg.degree≈p∗n. 

In addition, it generates directed networks, but you can ignore the directions of the links.]

In the G(n,p) model, the expected average degree is np http://cs.stackexchange.com/questions/39774/set-the-parameters-of-a-erdos-renyi-graph-generator-to-get-a-specific-mean-degre
.
```{r}
n <- 400

g1 <- sample_gnp(n, 1/n)
is.connected(g1)

g5 <- sample_gnp(n, 5/n)
is.connected(g5)

g10 <- sample_gnp(n, 10/n)
is.connected(g10)


g20 <- sample_gnp(n, 20/n)
is.connected(g20)
```
