---
title: "Problem Set 3"
output: 
  html_document: 
    theme: united
---

```{r message=FALSE}
library(igraph)
```
# Question 1
Consider the model of "Growing Random Networks" described in lecture 3.1 (so the first model where links are added to existing nodes uniformly at random), with m = 10.

At date t = 40, what are: 

(1) the expected degree for node 15 born at i = 15, and

(2) the expected degree for node 30 born at i = 30?

```{r}
m <- 10
t <- 40

d <- m * (1 + log(t/15))
round(d, 2)

d <- m * (1 + log(t/30))
round(d, 2)
```

# Question 2
Consider the "Preferential Attachment Model" described in lecture 3.3, 
with m = 10.

At date t = 40, what are:

(1) the expected degree for node 15 (born at time i = 15), and

(2) the expected degree for node 30 (born at time i = 30)?

[Hint: Use the approximation for the expected degree at time of a node 
born at time from the lecture 3.3.

You are encouraged to compare the results here to those in Question 1.]

```{r}
round(m * sqrt(t/15), 2)
round(m * sqrt(t/30), 2)

i <- 1:40
plot(m * sqrt(t/i), col='red', ylab='d')
points(i, m * (1 + log(t/i)), col='blue')
abline(v=15)
abline(v=30)
```

# Question 3
Consider the "Hybrid Model" described in lecture 3.4, with m = 10. Let us 
compare the cases of a = 0.8 and a = 0.2.

At date t = 10,000, consider a node born at date i = 20 and a node born at date i = 9999.

Recall the approximation of the expected degree at time t of a node born at time i.

Which option makes the following statement correct?

```{r}
t <- 10000

a <- c(0.8, 0.2)

i <- 9999
(m + 2*a*m/(1 - a))*(t/i)^((1-a)/2) - 2*a*m/(1 - a)
```

At date t = 10,000. a node born at date i=9,999 has a *higher* expected degree with a=0.8 than 
with a=0.2; and

```{r}
t <- 10000

a <- c(0.8, 0.2)

i <- 20
(m + 2*a*m/(1 - a))*(t/i)^((1-a)/2) - 2*a*m/(1 - a)
```

a node born at date i=20 has a *lower* expected degree with a=0.8 than 
with a=0.2.

# Questions 4 - 6
For questions 4 to 6, you are asked to estimate some ERGMs with the freeware "Statnet" within "R", which is also a free program. The dataset you will be using is "florentine.dat", which can be found florentine.dat

You can find instructions for the downloading and use of Statnet in the "statnet_instruction",
statnet_instruction.pdf

First, please use the software to estimate an Erdos-Renyi random graph, 
which is a special case of an ERGM where you fit only edges using the 
following command

Which of the following is the coefficient you got for edges?
```{r}
library(statnet)

# model1 <- ergm(flomarriage ~ edges)
```

